---
title: "Text Analysis"
output:
  pdf_document: default
  html_document: default
---

```{r}
pacman::p_load(tidyverse, tidytext, lubridate, stringr,
               gutenbergr, reshape2, wordcloud, textdata)

knitr::opts_chunk$set(echo = TRUE)

theme_set(theme_classic())

```



```{r}
load(file = 'song_lyrics.rda')
```



```{r}
tidy_books <- song_lyrics %>%
  unnest_tokens(word, lyrics)

```

```{r}
data("stop_words")
filter(stop_words, lexicon == "snowball")

tidy_books <- tidy_books %>%
  anti_join(stop_words)
```
# Qno. 1 Tokenize the lyrics variable, count the number of words in each song, and merge the total number of words in each song with the data (this will add a new column to the data). Print a few rows of the updated data set showing the total number of words in each song. 

## Ans:- 

```{r}
song_lyrics$Total_words <- sapply(song_lyrics$lyrics, 
                                  function(x) 
                                    length(unlist(strsplit(as.character(x), "\\W+"))))

head(song_lyrics,10)
```

# Qno. 2 Create sentiment scores using “bing” lexicon and count the number of sentiment words (number of positive and number of negative sentiment words, separately) in each song. 


```{r}
sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing"))
head(sentiment)
```


```{r}
sentiment %>%
count(sentiment, sort = TRUE)

sentiment %>%
  count(song, sentiment, sort = TRUE)
```


```{r}

sentiment_percentage <- sentiment %>%
  group_by(rank, song, artist, year)%>%
  mutate(total_sentiment_words = n())%>%
  group_by(rank, song, artist, year, sentiment, total_sentiment_words)%>%
  summarise(count=n())%>%
  mutate(percentage = round((count/total_sentiment_words)*100,2))

head(sentiment,20)
```

# Qno. 2(i) songs with the highest percentage of positive words;

```{r}
pos_per <- sentiment_percentage%>%
  filter(sentiment=="positive",percentage>50)%>%
  arrange(desc(percentage))

head(pos_per)
```


# Qno. 2(ii) songs with the highest percentage of positive words;

```{r}
neg_per <- sentiment_percentage%>%
  filter(sentiment=="negative", percentage>50)%>%
  arrange(desc(percentage))

head(neg_per)
```

# Qno. 3 Do songs with a higher percent of negative words rank higher on the Billboard chart (rank 1 is the highest and rank 100 is the lowest)? Answer this question by grouping songs in the following groups: 1-10, 11-20, …, and 91-100. Use boxplots for each of these groups, with ranking groups on the x axis and percent of negative words on the y axis.

## Ans:- The below plot explains that songs with rank 1-10 dont higher percentage of negative words. They have an average of 50% of negative words.

```{r}
sentiment_percentage$rank_group <- cut(sentiment_percentage$rank,
                                      breaks = c(0,10,20,30,40,50,60,70,80,90,100),
                                      labels = c("1-10", "11-20", "21-30", "31-40", "41-50",
                                                "51-60","61-70", "71-80", "81-90","91-100"))

negative_plot<- sentiment_percentage%>%filter(sentiment=="negative")
Rank_negative_plot <- ggplot(negative_plot,
    aes(x = rank_group, y = percentage, fill = rank_group))+
    geom_boxplot()+
    labs(title = "Percentage of negative words grouped over Decades",
              x = "Grouping by Rank",
              y = "Percentage of negative words")+
          scale_fill_brewer(palette="Paired")+
    theme(legend.position = "none")

Rank_negative_plot
```

# Qno. 4 Have the percent of positive words in a song increased over the decade? Answer this question by grouping songs over decades: 1960-1969, 1970-1979, …, 2010-2019. Use boxplots for each of these groups, with decades on the x axis and the percent of positive words on the y-axis.

## Ans:- The below plot explains, that every decade there is an average percent decrease of 4% in positive words. 

```{r}
sentiment_percentage$year_group <- cut(sentiment_percentage$year,
                                    breaks = c(-Inf,1969,1979,1989,1999,2009,2019),
                                    labels = c("1960-1969", "1970-1979","1980-1989",
                                    "1990-1999","2000-2009", "2010-2019"))

positive_plot <- sentiment_percentage%>%filter(sentiment=="positive")
Per_positive_words <- ggplot(positive_plot,
          aes(x = year_group, y = percentage, fill = year_group))+
          geom_boxplot()+
          labs(title = "Percentage of positive words grouped over Decades",
                x = "Grouping by Year",
                y = "Percentage of positive words")+
          scale_fill_brewer(palette="BuPu")+
          theme(legend.position = "none")

Per_positive_words
```

